%!TEX root = report.tex

\section*{Reference}
\small

[1] Yang, Yi, and Jacob Eisenstein. ``Overcoming Language Variation in Sentiment Analysis with Social Attention." arXiv preprint  arXiv:1511.06052 (2016).

[2] Perozzi, Bryan, Rami Al-Rfou, and Steven Skiena. ``Deepwalk: Online learning of social representations." Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2014.

[3] Tang, Jian, et al. ``Line: Large-scale information network embedding." Proceedings of the 24th International Conference on World Wide Web. ACM, 2015.

[4] Grover, Aditya, and Jure Leskovec. ``node2vec: Scalable feature learning for networks." Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. ACM, 2016.

[5] Tan, Chenhao, et al. ``User-level sentiment analysis incorporating social networks." Proceedings of the 17th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2011.

[6] Yang, Yi, and Ming-Wei Chang. ``S-mart: Novel tree-based structured learning algorithms applied to tweet entity linking." arXiv preprint arXiv:1609.08075 (2016).

[7] Yang, Yi, Ming-Wei Chang, and Jacob Eisenstein. ``Toward socially-infused information extraction: Embedding authors, mentions, and entities." arXiv preprint arXiv:1609.08084 (2016).

[8] Pang, Bo, and Lillian Lee. ``Opinion mining and sentiment analysis." Foundations and Trends® in Information Retrieval 2.1–2 (2008): 1-135.

[9] Kim, Yoon. "Convolutional neural networks for sentence classification." arXiv preprint arXiv:1408.5882 (2014).

[10] Dos Santos, Cícero Nogueira, and Maira Gatti. ``Deep Convolutional Neural Networks for Sentiment Analysis of Short Texts." COLING. 2014.

[11] Severyn, Aliaksei, and Alessandro Moschitti. ``Twitter sentiment analysis with deep convolutional neural networks." Proceedings of the 38th International ACM SIGIR Conference on Research and Development in Information Retrieval. ACM, 2015.

[12] Rosenthal, Sara, and Kathleen McKeown. ``Age prediction in blogs: A study of style, content, and online behavior in pre-and post-social media generations." Proceedings of the 49th Annual Meeting of the Association for Computational Linguistics: Human Language Technologies-Volume 1. Association for Computational Linguistics, 2011.

[13] Astudillo, Ramón Fernandez, et al. ``Learning Word Representations from Scarce and Noisy Data with Embedding Subspaces." ACL (1). 2015.

[14] Ling, Wang, et al. ``Two/Too Simple Adaptations of Word2Vec for Syntax Problems." HLT-NAACL. 2015.
APA	
